---
title: "One anastomosis gastric bypass (OAGB): Scoping review"
subtitle: "Deduplication"
author: 
  - name: Javier Mancilla-Galindo
    affiliation: Institute for Risk Assessment Sciences, Utrecht University, Utrecht, The Netherlands
    orcid: 0000-0002-0718-467X
    email: j.mancillagalindo@uu.nl
  - name: Jorge Alberto Guevara-Díaz
    affiliation: Medical Resident, Hospital General Regional No. 1, Instituto Mexicano del Servicio Social, Culiacan, Sinaloa, Mexico
    orcid: 0000-0002-9500-1780
keywords: ["Bariatric Surgery", "Obesity Management", "Gastric Bypass", "OAGB", "Mini gastric bypass", "diabetes remission", "Postoperative Complications"]
execute: 
  echo: false
  warning: false
toc: true
toc-depth: 1
format:
  html:
    toc: true
  docx:
    reference-doc: ../docs/manuscript/template.docx
  pdf:
    documentclass: scrartcl
editor: source
---

```{r}
#| label: directories
#| include: false

# Create directories for sub-folders  
inputfolder <- "../data/raw"
psfolder <- "../data/processed"
tempfolder <- "../data/temp"
figfolder <- "../results/output_figures"
tabfolder <- "../results/output_tables"

dir.create(inputfolder, showWarnings = FALSE)
dir.create(psfolder, showWarnings = FALSE)
dir.create(tempfolder, showWarnings = FALSE)
dir.create(figfolder, showWarnings = FALSE)
dir.create(tabfolder, showWarnings = FALSE)
```

```{r}
#| label: packages
#| include: false 

if (!require("pacman", quietly = TRUE)) {
  install.packages("pacman")
}

pacman::p_load(
  devtools,         # Used to install packages from GitHub.
  tidyverse,        # Used for basic data handling and visualization.
  readxl,           # Used to read excel files.
  overviewR,        # Used to check missing data.
  gt,               # Used to print html tables.  
  report            # Used to cite packages used in this session.   
)

pacman::p_load_gh("camaradesuk/ASySD")  # Used to deduplicate studies

```

# Databases searched

```{r}
#| label: embase

# Columns to select 
columns <- c("record_id", "author", "year", "journal", "doi", "title", "pages",
             "volume", "number", "abstract", "issn", "label", "source")

# Load embase data 
embase <- load_search(
  path = paste0(inputfolder, "/2025-05-28_Embase.ris"),
  method = "ris"
  ) %>% 
  mutate(
    abstract = N2,
    author = A1,
    issue = number,
    issn = isbn,
    year = Y1,
    title = T1,
    journal = JF,
    source = "embase"
  ) %>% 
  select(all_of(columns)) %>% 
  mutate_if(is.character, ~na_if(., ""))

```

```{r}
#| label: pubmed

# Load pubmed data 
pubmed <- load_search(
  path = paste0(inputfolder, "/2025-05-28_PubMed.csv"),
  method = "csv"
  ) %>% 
  mutate(
    source = "pubmed"
  ) %>% 
  select(all_of(columns)) %>% 
  mutate_if(is.character, ~na_if(., ""))

```

```{r}
#| label: web of science

wos <- read_excel(
  path = file.path(inputfolder, "2025-05-28_WoS.xlsx")
  ) %>% 
  mutate(
    record_id = NA,
    author = Authors,
    year = as.character(`Publication Year`),
    journal = `Source Title`,
    doi = DOI,
    title = `Article Title`,
    pages = paste0(`Start Page`, "-", `End Page`),
    volume = as.character(Volume),
    number = Issue,
    abstract = Abstract,
    issn = ISSN,
    label = NA_character_,
    source = "wos"
  ) %>% 
  mutate(pages = gsub("-\\+", "", pages),      
                 pages = ifelse(pages == "NA-NA", NA_character_, pages)) %>% 
  select(all_of(columns))

```

There are a total of `r count(embase)` records in Embase, `r count(pubmed)` records in PubMed, and `r count(wos)` records in Web of Science.

A plot of missing data for corroboration before deduplication is shown in **Figure 1**. Missing data should be lower than 100% for all variables, except for `record_id` and `label`, which are optional. Overall, **PubMed** has the least amount of missing data, so it will be used as the preferred source to keep in the deduplication procedure to minimize the amount of manual corroborations needed.

```{r}
#| label: missing
#| fig-cap: "**Figure 1**. Missing data per database"
#| fig-subcap:
#|   - "PubMed"
#|   - "Embase"
#|   - "WoS"
#| layout-ncol: 1

overview_na(pubmed)
overview_na(embase)
overview_na(wos)
```

```{r}
#| label: merge
# Bind Embase, PubMed, and Web of Science 
records <- bind_rows(
  embase, 
  pubmed,
  wos
  )

```

There are a total of `r count(records)` records. These will be deduplicated using the Automated Systematic Search Deduplicator (ASySD).

```{r}
#| label: deduplication

# Deduplicate studies
deduplicated <- dedup_citations(
  records, 
  keep_source = "pubmed",
  manual_dedup =  TRUE,
  show_unknown_tags = FALSE,
  user_input = 1
  )

records_unique <- deduplicated$unique 
records_manual_dedup <- deduplicated$manual_dedup %>% 
  mutate(
    result = case_when(
      doi == 1 ~ TRUE, 
      TRUE ~ NA
    )
  )

```


```{r}
#| eval: FALSE

true_dups <- manual_dedup_shiny(records_manual_dedup)
saveRDS(true_dups, file = paste0(tempfolder, "/", lubridate::today(),"_true_duplicates.rds"))
```


```{r}
true_dups <- read_rds(paste0(tempfolder, "/2025-05-28_true_duplicates.rds"))

records_final_dedup <- dedup_citations_add_manual(records_unique, additional_pairs = true_dups)
```

```{r}
#| include: false 

# There are remaining duplicates by doi 
records_final_dedup %>% 
  group_by(doi) %>% 
  mutate(n = n()) %>% 
  filter(n > 1 & !is.na(doi)) %>%
  ungroup() %>% 
  arrange(doi) %>% 
  summarize(n = n())
```


```{r}
# Filter out rows with NA DOI first
dedup_part <- records_final_dedup %>%
  filter(!is.na(doi)) %>%
  mutate(
    source_priority = case_when(
      str_detect(source, "pubmed") ~ 1,
      str_detect(source, "wos") ~ 2,
      str_detect(source, "embase") ~ 3,
      TRUE ~ 4
    )
  ) %>%
  group_by(doi) %>%
  arrange(source_priority) %>%
  summarise(
    across(
      .cols = -c(source, record_ids, source_priority),
      .fns = ~ first(.)
    ),
    source = paste(source, collapse = ", "),
    record_ids = paste(record_ids, collapse = ", "),
    .groups = "drop"
  )

# Add back rows with NA in doi (which are skipped in deduplication)
dedup_na_part <- records_final_dedup %>%
  filter(is.na(doi))

# Combine both
records_final_unique <- bind_rows(dedup_part, dedup_na_part)

```



```{r}
write_citations(
  records_final_unique,
  type = "csv",
  filename = paste0(psfolder, "/", lubridate::today(), "_search_deduplicated.csv")
)
```

After deduplication, there are a total of `r count(records_final_unique)` studies. 

{{< pagebreak >}}

# ASReview labels

Labels from prior ASReview sessions were imported and merged with the new data. The final datasets are found in the psfolder.

```{r}
#| include: false
suffixes <- c("complications", "GERD", "remission", "weight_loss")

for (s in suffixes) {
  data <- readr::read_csv(paste0("../data/raw/asreview_", s, ".csv"))
  assign(paste0("asreview_", s), data)
}
```

```{r}
for (s in suffixes) {
  asreview_df <- get(paste0("asreview_", s))
  
  final_df <- records_final_unique %>%
    # Join only where doi is not NA
    left_join(
      asreview_df %>%
        filter(!is.na(doi)) %>%
        select(doi, asreview_prior, included, asreview_ranking, exported_notes_1),
      by = "doi"
    )
  
  assign(paste0("final_asreview_", s), final_df)
}
```

```{r}
# Loop and save each final data frame
for (s in suffixes) {
  final_df <- get(paste0("final_asreview_", s))
  file_name <- paste0(psfolder, "/", today(), "_asreview_final_", s, ".csv")
  write_csv(final_df, file_name)
}
```

{{< pagebreak >}}

# Session Information

```{r}
#| label: session
# remove clutter
session <- sessionInfo()
session$BLAS <- NULL
session$LAPACK <- NULL
session$loadedOnly <- NULL
# write log file
writeLines(
  capture.output(print(session, locale = FALSE)),
  paste0("sessions/",lubridate::today(), "_deduplication.txt")
)                                   

session
```

{{< pagebreak >}}

# Package References

```{r}
#| output: asis
report::cite_packages(session)
```

```{r}
#| include: false

# Run this chunk if you wish to clear your environment and unload packages.

pacman::p_unload(negate = TRUE)

rm(list = ls())
```
